---
title: "Practical Machine Learning"
author: "Vanja Čotić Poturić"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

### Summary

In this project, we use data of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways.The goal of this project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 


### Data

```{r,echo = FALSE}

library(caret)
library(RColorBrewer)
library(randomForest)
library(rattle)
library(lattice)
library(ggplot2)
library(rpart)
library(rpart.plot)

training<-read.csv("C:/Users/Admin/Downloads/pml-training.csv",na.strings=c("NA","#DIV/0!",""))
testing<-read.csv("C:/Users/Admin/Downloads/pml-testing.csv",na.strings=c("NA","#DIV/0!",""))

head(training[156:160])
unique(training$classe)
unique(training$user_name)

```
### Data cleaning
```{r}
NA_Count = sapply(1:dim(training)[2],function(x)sum(is.na(training[,x])))
NA_list = which(NA_Count>0)
training = training[,-NA_list]
training = training[,-c(1:7)]
testing = testing[,-NA_list]
testing = testing[,-c(1:7)]
dim(testing)
dim(training)
table(training$classe)
```

## Cross Validation


### LDA

```{r}

set.seed(1234)
lda_model<-train(classe~ .,method="lda", data=training)
predict_lda<-predict(lda_model,training)
confusionMatrix(predict_lda,as.factor(training$classe))
```

### Decision Tree

```{r}
library(rattle)
set.seed(1357)
dt_model <- train(classe ~., method = "rpart", data = training)
predict_dt<-predict(dt_model,training)
confusionMatrix(predict_dt,as.factor(training$classe))

```

### Random Forest

```{r}
set.seed(2468)
rf_model <- train(classe ~., method = "rf", data = training)
predict_rf<-predict(rf_model,training)
confusionMatrix(predict_rf,as.factor(training$classe))
```
The Random Forest model is selected because it has the largest accuracy.
```{r}
predict <- predict(rf_model, testing)
predict
```
